### 2010-01-15 docs/algdraft/Materialize_DB.tex
add mime type to these two files.

\documentclass[10pt]{article}
%\title{}
%\author{}
%\date{}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{a4}
\usepackage{color}
\renewcommand\floatpagefraction{0.99}
\renewcommand\topfraction{0.99}
\renewcommand\bottomfraction{0.99}
\renewcommand\textfraction{.05}
\setcounter{totalnumber}{5}
%\setlength{\parindent}{0pt}
%\pdfpagewidth 8.5in
%\pdfpageheight 11in

\begin{document}

@@

For Row(2007, 1, piru, 35.8)
    \begin{itemize}
    \item Create a measurement $mi_1=\langle meas1, null, Year, 2007\rangle$
    \item Create a measurement $mi_2=\langle meas2, null, Year, 35.8\rangle$
    \item Create a measurement $mi_3=\langle meas3, null, TaxonomicTypeName, Picea~rubens\rangle$
    \item Create a measurement $mi_4=\langle meas4, null, EntityName, 1\rangle$
    \item Get $MeasSet = \{mi_1, mi_2, mi_3, mi_4\}$;
    \item Step 2: Get $KeyIdx = \{o_1\rightarrow \{mi_1\}, o_2 \rightarrow \{mi_2, mi_3, mi_4\}\}$
    \item Step 3-4: for each observation types $o_1$ and $o_2$
    \item for $o_1$
    \begin{itemize}
        \item Since $m_1$ is specified as key, get the $KeyVal=2007$;
        \item No entity with this key exists in $EntIdx$, create an entity $ei=\langle ent1, TemporalRange\rangle$; Now, $EntIdx=\{\langle o1, 2007\rightarrow ent1\rangle\}$.
        \item Since $o_1$ is specified as {\em distinct}, need to make sure we do not create redundant observations. No entry with this key exists in $ObsIdx$, so, create an observation
        $oi = \langle obs1, ent1\rangle$. Now, $ObsIdx=\{\langle o1, 2007 \rangle \rightarrow obs1\}$
    \end{itemize}
    \item When deal with $o_2$,
        \begin{itemize}
        \item $KeyVal=1$.
        \item Create an entity $ei=\langle ent2, Tree\rangle$; $EntIdx=\{\langle o1, 2007\rightarrow ent1\rangle, \langle o2, 1\rightarrow ent2\rangle\}$.
        \item Create an observation $\langle obs2, ent2 \rangle$. No need to update $ObsIdx$ because $o2$ is not identified as {\em unique}.
        \end{itemize}
    \item Connect $mi_1$ to $obs1$;
    \item Connect $mi_2$, $mi_3$ and $mi_4$ to $obs2$;
    \item Set the context relationship between $obs1$ and $obs2$;
    \end{itemize}

@@

>>>>

\documentclass[10pt]{article}
%\title{}
%\author{}
%\date{}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{a4}
\usepackage{color}
\renewcommand\floatpagefraction{0.99}
\renewcommand\topfraction{0.99}
\renewcommand\bottomfraction{0.99}
\renewcommand\textfraction{.05}
\setcounter{totalnumber}{5}
%\setlength{\parindent}{0pt}
%\pdfpagewidth 8.5in
%\pdfpageheight 11in
\newtheorem{example}{Example}[section]
\begin{document}

@@

For Row(2007, 1, piru, 35.8)
    \begin{itemize}
    \item Create a measurement $mi_1=\langle meas1, null, Year, 2007\rangle$
    \item Create a measurement $mi_2=\langle meas2, null, DBH, 35.8\rangle$
    \item Create a measurement $mi_3=\langle meas3, null, TaxonomicTypeName, Picea~rubens\rangle$
    \item Create a measurement $mi_4=\langle meas4, null, EntityName, 1\rangle$
    \item Get $MeasSet = \{mi_1, mi_2, mi_3, mi_4\}$;
    \item Step 2: Get $KeyIdx = \{o_1\rightarrow \{mi_1\}, o_2 \rightarrow \{mi_2, mi_3, mi_4\}\}$
    \item Step 3-4: for each observation types $o_1$ and $o_2$
    \item for $o_1$
    \begin{itemize}
        \item Since $m_1$ is specified as key, get the $KeyVal=2007$;
        \item No entity with this key exists in $EntIdx$, create an entity $ei=\langle ent1, TemporalRange\rangle$; Now, $EntIdx=\{\langle o1, 2007\rightarrow ent1\rangle\}$.
        \item Since $o_1$ is specified as {\em distinct}, need to make sure we do not create redundant observations. No entry with this key exists in $ObsIdx$, so, create an observation
        $oi = \langle obs1, ent1\rangle$. Now, $ObsIdx=\{\langle o1, 2007 \rangle \rightarrow obs1\}$
    \end{itemize}
    \item When deal with $o_2$,
        \begin{itemize}
        \item $KeyVal=1$.
        \item Create an entity $ei=\langle ent2, Tree\rangle$; $EntIdx=\{\langle o1, 2007\rightarrow ent1\rangle, \langle o2, 1\rightarrow ent2\rangle\}$.
        \item Create an observation $\langle obs2, ent2 \rangle$. No need to update $ObsIdx$ because $o2$ is not identified as {\em unique}.
        \end{itemize}
    \item Connect $mi_1$ to $obs1$;
    \item Connect $mi_2$, $mi_3$ and $mi_4$ to $obs2$;
    \item Set the context relationship between $obs1$ and $obs2$;
    \end{itemize}

@@

\begin{table}[htb]
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
plt & spp & dbh\\\hline
A & piru & 35.8 \\\hline
A & piru & 36.2 \\\hline
B & piru &33.2 \\\hline
\end{tabular}
\end{center}
\vspace{-0.2in}
\caption{Dataset 2 for Example \ref{eg2}}
\end{table}

\begin{example} [Example with identifying]\label{eg2}
Use the data in the following table as an example.

For the {\bf first row}, after we run the first step, we got the three measurement instances $MeasSet=mi_1, mi_2, mi_3$. 
After the second step, we get $KeyIdx = \{\langle o_1\rightarrow \{mi_1\} \rangle, \langle o_2 \rightarrow \{mi_2, mi_3\}\}$.

Now we need to create observation and entity instances. 
To create entity instance, we need to see whether there is/are key measurements for each observatioin type.  
Here,  $o_1$ and $o_2$ have key measurements $m1$ and $m_2$ respectively. 
The same value of the key measurement will denote the same entity. 
For $o_1$, we get it's key value be $A$. Since there is no such a statement, we create an entity $ei_1$ of type $Plot$.
Simiarly, for $o_2$, the key value is $(A, Picea~rubens)$ since it has context $o_1$ with {\em identifying yes}, we create an entity $ei_2$ of type $Tree$. \\
$EntIdx = \{\langle o_1, A\rangle \rightarrow ei_1, \langle o_2, (A, Picea~rubens) \rangle \rightarrow ei_2\}$.

To create observation instance, we need to see whethe the observation type is specified with distinct yes. 
Here, $o_1$ is specified with {\em distinct yes} while $o_2$ is not. 
We only check whether we need to merge observation instances for $o_1$ or not. 
We create an observation instance $oi_1$ whose entity is $ei_1$. 
We also create an observation instance $oi_2$ whose entity is $ei_2$. 
$ObsIdx = \{\langle o_1, A\rangle \rightarrow oi_1\}$.

The next step is to connect the measurement instances to observation instances,  $mi_1 \rightarrow oi_1$, $mi_2, mi_3 \rightarrow oi_2$.

The last step for this row is to connect the observations using context relationship. For this instance, we connect $oi_1$ to $oi_2$ with context {\em Within}.

For the {\bf second row}, after the first step, we also get three measurement instances $MeasSet=mi_4, mi_5, mi_6$. 
After the second step, we get $KeyIdx = \{\langle o_1\rightarrow \{mi_4\} \rangle, \langle o_2 \rightarrow \{mi_5, mi_6\}\}$.

When we create entities, 
we need to check whether there is any entity corresponding to Key value $\langle o_1, A\rangle$ $\langle, o_2, (A, Picea~rubens)\rangle$ or not.
We observe that they have corresponding $ei_1$ and $ei_2$. So, we don't need to create entity instances for them.

Now, we create observatins, 
Since $o_1$ is specified with {\em distinct yes}, we just need to see whether we need to create a new observation for it or get an existing one. 
The key is $\langle o_1,A\rangle$, which corresponds to $oi_1$. So, we do not need to create a new observation for it. 
For $o_2$, since no {\em distinct yes} is specified, we create an observation $oi_3$ for it.

For the next step, when we try to connect the measurement instances to observation instances, we realize that we do not create a new observation for $o_1$,
so it's related measurement instance $mi_4$ can be discarded. While for $o_2$, $m_5, m_6\rightarrow oi_3$.

When we process the {\bf third row}, one thing to note is for $o_1$, now we have key value $\langle o_1, B\rangle$, we create a new entity for it.
For $o_2$, we have key value $\langle o_2, (B,~Picea~rubens)\rangle$ and create a new entity for it.

\end{example}
